Pre-/Post-Trikafta in CFRD

### 2025-01-02 Colleen Wood/Pre-post Trikafta/pre_post_trikafta_analysis.qmd
minor formatting changes for Colleen

---
title: "Pre-/Post-Trikafta in CFRD"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpmisc)
library(lubridate)
library(gtsummary)
library(knitr)
library(rspiro)
library(lmerTest)
library(car)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Colleen Wood"
)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
#| include: false
load("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood/Prepost Trikafta/Data_Cleaned/analysis_dataset.rdata")
load("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood/Prepost Trikafta/Data_Cleaned/hba1c_dataset.rdata")
# Ethnicity
chco_demo <- read.csv("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood/Prepost Trikafta/Data_Raw/Data From CHCO/Registry/Copy of Earliest Trikafta Dates in Registry_updated 2.2.21 cc modified_cfrdyn.csv")
chco_demo$Hispanic <- NA
chco_demo$Hispanic[chco_demo$Hispanic.Latinx] <- "Yes"
chco_demo$Hispanic[!chco_demo$Hispanic.Latinx] <- "No"
chco_demo <- chco_demo[, c("CFF.ID", "Hispanic")]
montana_demo <- read.csv("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood/Prepost Trikafta/Data_Cleaned/montana_demo.csv")
montana_demo$Hispanic <- montana_demo$Is.Patient.of.Hispanic.Origin
montana_demo <- montana_demo[, c("CFF.ID", "Hispanic")]
uw_demo <- read.csv("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood/Prepost Trikafta/Data_Cleaned/uw_demo.csv")
uw_demo$Hispanic <- uw_demo$Is.Patient.of.Hispanic.Origin
uw_demo <- uw_demo[, c("CFF.ID", "Hispanic")]
eth <- do.call(rbind, list(chco_demo, montana_demo, uw_demo))
colnames(eth) <- c("CFF ID", "Hispanic")
df <- left_join(df, eth)
```

>>>>

---
title: "Pre-/Post-Trikafta in CFRD"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/Dropbox/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpmisc)
library(lubridate)
library(gtsummary)
library(knitr)
library(rspiro)
library(lmerTest)
library(car)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Colleen Wood")
```

```{r data cleaning}
#| include: false
load("./Prepost Trikafta/Data_Cleaned/analysis_dataset.rdata")
load("./Prepost Trikafta/Data_Cleaned/hba1c_dataset.rdata")
# Ethnicity
chco_demo <- read.csv("./Prepost Trikafta/Data_Raw/Data From CHCO/Registry/Copy of Earliest Trikafta Dates in Registry_updated 2.2.21 cc modified_cfrdyn.csv")
chco_demo$Hispanic <- NA
chco_demo$Hispanic[chco_demo$Hispanic.Latinx] <- "Yes"
chco_demo$Hispanic[!chco_demo$Hispanic.Latinx] <- "No"
chco_demo <- chco_demo[, c("CFF.ID", "Hispanic")]
montana_demo <- read.csv("./Prepost Trikafta/Data_Cleaned/montana_demo.csv")
montana_demo$Hispanic <- montana_demo$Is.Patient.of.Hispanic.Origin
montana_demo <- montana_demo[, c("CFF.ID", "Hispanic")]
uw_demo <- read.csv("./Prepost Trikafta/Data_Cleaned/uw_demo.csv")
uw_demo$Hispanic <- uw_demo$Is.Patient.of.Hispanic.Origin
uw_demo <- uw_demo[, c("CFF.ID", "Hispanic")]
eth <- do.call(rbind, list(chco_demo, montana_demo, uw_demo))
colnames(eth) <- c("CFF ID", "Hispanic")
df <- left_join(df, eth)
```
